R Notebook

### 2022-11-16 Scripts/data_cleaning.Rmd
Various changes to add new Nelda and MassMob variables; moved MassMob models to appendix 2

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda29)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda27)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)

@@

nelda <- nelda %>% mutate(inc.termlimit.num = ifelse(types == "Legislative/Parliamentary" & inc.termlimit == "N/A", 0, ifelse(types == "Executive" & inc.termlimit == "yes", 1,                                                                                                                       ifelse(types == "Executive" & inc.termlimit == "no", 0, NA))))

@@

nelda3 <- nelda %>% dplyr::select(ccode, country, year, electionid, election_mdy)
nelda3 <- nelda3 %>% mutate(election_year = year)
nelda3 <- massmob %>% left_join(nelda3, by = c("ccode", "year")) #Nelda3 is in progress, need to figure out a) if needed, b) how to include pre-election and post-election mobilization
```

@@

size_data_mm_pre <- nelda3.sub.pre %>% group_by(electionid) %>% summarize(median.participants.pre = median(participants_category_ordered, na.rm = T))
size_data_mm_post <- nelda3.sub.post %>% group_by(electionid) %>% summarize(median.participants.post = median(participants_category_ordered, na.rm = T))

@@

```{r}
winner.shares <- read.csv(here::here("Data", "amended_vote_shares.csv"))
nelda2.sub <- nelda2.sub %>% left_join(winner.shares, by = "NeldaID")
```

@@

nelda2.sub <- nelda2.sub %>% left_join(mm_data_comb, by = "NeldaID")  ## Double check to make sure this joining works

>>>>

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda29)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda27)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)

@@

nelda <- nelda %>% mutate(inc.termlimit.num = ifelse(types == "Legislative/Parliamentary" & inc.termlimit == "N/A", 0, ifelse(types == "Executive" & inc.termlimit == "yes", 1,                                                                                                                       ifelse(types == "Executive" & inc.termlimit == "no", 0, NA))))
nelda <- nelda %>% mutate(preelection_concerns = ifelse(preelection_concerns == "yes", 1, ifelse(preelection_concerns == "no", 0, NA)))
nelda <- nelda %>% mutate(harass_opp = ifelse(nelda3 == "No", 1, ifelse(harass_opp == "yes", 1, ifelse(harass_opp == "no", 0, NA))))
nelda <- nelda %>% mutate(opp_leaders_prevented = ifelse(nelda3 == "No", "In general", ifelse(opp_leaders_prevented == "yes", "Specifically", ifelse(opp_leaders_prevented == "no", "No", NA))))

@@

nelda3 <- nelda %>% dplyr::select(ccode, country, year, electionid, election_mdy)
nelda3 <- nelda3 %>% mutate(election_year = year)
nelda3 <- massmob %>% left_join(nelda3, by = c("ccode", "year"))
```

@@

size_data_mm_pre <- nelda3.sub.pre %>% group_by(electionid) %>% summarize(median.participants.mm.pre = median(participants_category_ordered, na.rm = T))
size_data_mm_post <- nelda3.sub.post %>% group_by(electionid) %>% summarize(median.participants.mm.post = median(participants_category_ordered, na.rm = T))

@@

@@

nelda3.sub <- nelda2.sub %>% left_join(mm_data_comb, by = "NeldaID")  ## Double check to make sure this joining works

## Code NAs for number of protests as 0s (these reflect election years recorded in NELDA where there were no protests recorded by MM)

nelda3.sub <- nelda3.sub %>% mutate(n.events.massmob.pre = ifelse(is.na(n.events.massmob.pre)==T, 0, n.events.massmob.pre))
nelda3.sub <- nelda3.sub %>% mutate(n.events.massmob.post = ifelse(is.na(n.events.massmob.post)==T, 0, n.events.massmob.post))

nelda3.sub <- nelda3.sub %>% mutate(median.participants.mm.pre = ifelse(is.na(median.participants.mm.pre)==T & n.events.massmob.pre == 0, 0, median.participants.mm.pre))
nelda3.sub <- nelda3.sub %>% mutate(median.participants.mm.post = ifelse(is.na(median.participants.mm.post)==T & n.events.massmob.post == 0, 0, median.participants.mm.pre))

## Rounding participant median numbers down (removes half-steps)

nelda3.sub <- nelda3.sub %>% mutate(median.participants.mm.post = floor(median.participants.mm.post))
nelda3.sub <- nelda3.sub %>% mutate(median.participants.mm.pre = floor(median.participants.mm.pre))

```{r}
winner.shares <- read.csv(here::here("Data", "amended_vote_shares.csv"))
nelda2.sub <- nelda2.sub %>% left_join(winner.shares, by = "NeldaID")
nelda3.sub <- nelda3.sub %>% left_join(winner.shares, by = "NeldaID")
